Applying Renormalization Group Theory to the Square Well Liquid

### 2014-07-11 papers/thesis-roth/project.tex
Copied important files from thesis-roth to renormalization. Added fig comparing grand free energy for various iteration depths Tested on elliot. Took 0:33.68.

One particularly troublesome regime is around the critical
point of a liquid. At the appropriate density and temperature, the
distinction between liquid and vapor disappears. Beyond this point,
you have a ``supercritical fluid.'' Supercritical fluids are used in
many industrial processes.\cite{Perrut00} For example (and of personal
interest), supercritical fluids are used in coffee decaffeination and
the extraction of hops resins for brewing beer.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistence_SW}
  \end{center}
  \caption{Liquid-vapor coexistence for a square well liquid.}
  \label{fig:coexistance_SW}
\end{figure}

Figure~\ref{fig:coexistance_SW} is a demonstration of this algorithm.

>>>>

One particularly troublesome regime is around the critical point of a
liquid. At the appropriate density and temperature, the distinction
between liquid and vapor disappears. Beyond this point, you have a
``supercritical fluid.'' Supercritical fluids are used in many
industrial processes.\cite{Perrut00} For example, supercritical fluids
are used in coffee decaffeination and the extraction of hops resins
for brewing beer.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{figs/coexistence_SW}
  \end{center}
  \caption{Liquid-vapor coexistence for a square well liquid.}
  \label{fig:coexistence_SW}
\end{figure}

Figure~\ref{fig:coexistence_SW} is a demonstration of this algorithm.
